\textit{Rubrics Criteria:}
\begin{itemize}
    \item \textbf{Organization and Structure} (out of 3 marks)
    \begin{enumerate}
        \item Does the submission provide a runnable implementation source code?
            \answerTODO{}
        \item Does the write-up mention all required sections: \texttt{Abstract}, \texttt{Task Definition}, \texttt{Infrastructure}, \texttt{Approach}, \texttt{Literature Review}, \texttt{Experiments and Analysis}, \texttt{Contributions}, \texttt{References}?
            \answerTODO{}
        \item Does the write-up adhere to the maximum eight page limit for the report requirement (0.5 marks will be deducted for each extra page; main sections and all the relevant results must be placed in these eight pages)?
            \answerTODO{}
    \end{enumerate}
    \item \textbf{Content} (out of 44 marks)
    \begin{itemize}
        \item \texttt{Abstract} (out of 3 marks)
        \begin{enumerate}
            \item Does the abstract contain 200 words or less?
                \answerTODO{}
            \item Does it explain what is the write-up about?
                \answerTODO{}
            \item Does it explain the key findings of the project?
                \answerTODO{} 
        \end{enumerate}
        \item \texttt{Task Definition} (out of 3 marks)
        \begin{enumerate}
            \item Does it provide the problem statement?
                \answerTODO{}
            \item Does it provide the evaluation metrics?
                \answerTODO{}
            \item Does it refrain from putting anything related to the solution, implemented source code, results and analysis?
                \answerTODO{}
        \end{enumerate}
        \item \texttt{Infrastructure} (out of 2 marks) 
        \begin{enumerate}
            \item Does it properly discuss the infrastructure used and required for running the code?
            \answerTODO{}
            \item Does it provide information and guidelines on how to run the code in both train and inference modes?
            \answerTODO{}
        \end{enumerate}
        \item \texttt{Approach} (out of 8 marks)
        \begin{enumerate}
            \item Does it explain the procedure that transforms the raw \texttt{json} records to the instances that can be fed to the models (out of 3 marks)?
            \answerTODO{}
            \item Does the it explain how the data transformation procedure differs in training and inference modes?
            \answerTODO{}
            \item Does it mention the different modelling techniques used in part 2 (at least on per group member and each from a different model class based on the project requirements), and explain how each technique is used to perform the task of sentiment analysis (out of 4 marks)?
                \answerTODO{}
        \end{enumerate}
        \item \texttt{Literature Review} (out of 3 marks) 
        \begin{enumerate}
            \item Does it discuss other places and possibly publications that have tried tackling this task (out of 3 marks; at least one paper per group member must be discussed; websites and weblog articles do not count towards this requirement)?
                \answerTODO{}
        \end{enumerate}
        \item \texttt{Experiments and Analysis} (out of 22 marks)
        \begin{enumerate}
            \item Does it provide the base experiment results for the neural network design as well as the process of finding the best settings for it (out of 3 marks)?
                \answerTODO{}
            \item Does it provide two distinct experiments the neural network model, analyze the results, and explain what you learned (out of 4 marks)?
                \answerTODO{}
            \item Does it provide the base experiment results for the probabilistic model design as well as the process of finding the best settings for it (out of 3 marks)?
                \answerTODO{}
            \item Does it provide two distinct experiments the probabilistic model, analyze the results, and explain what you learned (out of 4 marks)?
                \answerTODO{}
            \item Does it provide the base experiment results for the other model class design as well as the process of finding the best settings for it (out of 3 marks)?
                \answerTODO{}
            \item Does it provide two distinct experiments for the other model class, analyze the results, and explain what you learned (out of 4 marks)?
                \answerTODO{}
            \item Do the Sentiment Analysis experiment results show F1 scores above 0.5? 
                \answerTODO{}
        \end{enumerate}
        \item \texttt{Contributions} (out of 1 mark)
        \begin{enumerate}
            \item Does it provide enough explanations on the contributions of each member as well as the contribution percentage?
                \answerTODO{}
        \end{enumerate}
        \item \texttt{References} (out of 2 marks)
        \begin{enumerate}
            \item Is each bibliography item cited at least once in the write-up?
                \answerTODO{}
            \item Is bibliography/citation format consistent across the write-up and the write-up follows a standard bibliography style?
                \answerTODO{}
        \end{enumerate}
    \end{itemize}
    \item \textbf{Readability} (out of 5 marks)
    \begin{enumerate}
        \item Does the write-up have any spelling errors?
            \answerTODO{}
        \item Does the write-up have any grammar errors?
            \answerTODO{}
        \item Does the write-up have a proper and logical flow of information (grade out of 3)?
            \answerTODO{}
    \end{enumerate}
    \item \textbf{Total Grade}: out of the 52 marks, what would be a fair grade for your submission from your point of view?
        \answerTODO{}
    \item \textbf{Important Note}: I will consider 10\% penalty over your total grade if your submission lacks a completed version of this rubrics section.
\end{itemize}
